Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
ok

TODO Miten paperinkulutus suhtautuu dokumenttien määrään? Löydetäänkö
ajankohtia jolloin on poikkeuksellista kasvua / laskua
tms. Esim. top-10 julkaisupaikat.

How over 50 page documents are spreading in time. Paper consumption in
books (over 50 pages; balls) versus other documents (less or equal
than 50 pages; triangles). TODO: voidaanko tässä nähdä paikallisia
eroja ?

@@

Gatherings vs. pagecounts per country (Fennica)

```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
selected.countries = c("Finland", "Sweden")
dfs <- fen %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()
p <- ggplot(dfs, aes(x = pagecount, y = gatherings, size = n)) +
     geom_point() + facet_grid(country ~ .) + scale_x_log10()
print(p)
```

Title count and overall paper consumption in the top publication locations (Fennica). The current country of origin is indicated. Finland is highlighted. Note that paper consumption estimates have still problems.

```{r LIBER-8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=8}
df <- fen
theme_set(theme_bw(20))
top <- names(rev(sort(table(df$publication_place))))[1:50]
dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_place) %>% summarize(titles = n(), paper = sum(paper.consumption.km2, na.rm = T))
dfs$country <- get_country(dfs$publication_place)
dfs$finland <- dfs$country == "Finland"
p <- ggplot(dfs, aes(x = titles, y = paper))
p <- p + geom_text(aes(label = publication_place, color = finland), size = 5)
p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
p <- p + scale_color_manual(values = c("darkgray", "black"))
p <- p + guides(color = "none")
p <- p + scale_x_log10() + scale_y_log10() 
p <- p + ggtitle("Title count versus paper (places)")
print(p)	 
```

>>>>

Paper consumption per document in the top publication places. Note
that paper consumption estimates have still problems so take this with
reservations. Are there time periods with remarkable changes in paper
consumption per document (meaning that small or large volumes suddenly
become more frequent) ?

```{r bookmedia2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
for (catal in unique(df0$catalog)) {
  df <- subset(df0, catalog = catal)
  theme_set(theme_bw(20))
  top <- names(top(df, "publication_place", 10))

  dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_decade, publication_place, country) %>% summarize(n = n(), paper = sum(paper.consumption.km2, na.rm = T))  %>% mutate(paper.per.document = paper/n)

  p <- ggplot(dfs, aes(x = publication_decade, y = paper.per.document)) +
       geom_point(aes(color = publication_place, shape = publication_place)) +
       geom_line(aes(color = publication_place, linetype = publication_place)) +
       xlab("Title Count") + 
       ggtitle(paste("Paper consumption per document\n", catal)) +
       scale_y_log10() 
  #p <- p + geom_text(aes(label = publication_place), size = 5)
  #p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
  #p <- p + scale_color_manual(values = c("darkgray", "black"))
  #p <- p + guides(color = "none")
  print(p)	 
}
```

Overview on how over 50 page documents spread in time. Paper
consumption in books (over 50 pages; balls) versus other documents
(less or equal than 50 pages; triangles). TODO: voidaanko tässä nähdä
paikallisia eroja ?

@@
